Regular singular Volterra equations on complex domains

### 2024-04-30 sima/reg-sing-volterra_sima.tex
Work on definitions of weighted L-infinity spaces
Also do other revisions, like condensing the outline of the main argument.

Throughout this paper, as described in Section~\ref{motivation}, the \textcolor{magenta}{``}position\textcolor{magenta}{'' [why are these quote marks nencessary? we've already introduced the term ``position'']} variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$. \textcolor{red}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$. Give $\cont(\domain)$ the compact-open topology, recalling that this} \textcolor{blue}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology. This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}. The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.

@@

@@

Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{\sigma}{\Lambda}(\Omega)$. This sequence is Cauchy in $\holo(\Omega)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ says that for any $r > 0$, there is some $n$ for which $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$. Since convergence in $\holo(\Omega)$ implies pointwise convergence, it follows that $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| \le r$. This reasoning shows that $f_1, f_2, f_3, \ldots$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$. It also shows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we have
\begin{align*}
|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{\sigma,\Lambda}
\end{align*}
for the corresponding $n$, so $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f|$ is bounded.
\end{proof}
\color{red}
\begin{proposition}%%\label{exp-complete}
The space $\singexp{0}{\Lambda}(\domain)$ is complete.
\end{proposition}
\begin{proof}
Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

@@

Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$. \color{red} For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$. Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$. Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we \textcolor{red}{can} generalize Proposition~\ref{exp-complete}:
\color{brown}
For $\sigma\in\R$, let 
\[\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|\,,\qquad f\in\holo(\domain)\,.\]
\begin{definition}
    We define the normed space
    \[\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega):=\{f\in\holo(\domain)\,\vert \, \|f\|_{\sigma,\Lambda}<+\infty\}\,.\]
\end{definition}
\begin{rmk}
    The above is a space of functions uniformly bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda |\zeta|}$.
\end{rmk}
\color{black}
\begin{proposition}
The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
\end{proposition}
\color{brown}
\begin{proof}
Let $\{f_n\}_{n=1}^\infty\subset\singexp{\sigma}{\Lambda}(\domain)$ be a Cauchy sequence. The inclusion map $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each norm on $\sup_K |f|$ on $\holo(\domain)$, where $K \subset \Omega$ is compact. Hence, $\{f_n\}_{n=1}^\infty$ is a Cauchy sequence also in $\holo(\domain)$. The latter being complete~\cite[Proposition~3.5]{fnl-cpx-anal}, the sequence converges to a function $f\in\holo(\domain)$.

By the Cauchy property on $\singexp{\sigma}{\Lambda}(\Omega)$, for any $r > 0$ there exists $n$ such that $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ for every $k \ge n$. Since convergence in $\holo(\Omega)$ implies pointwise convergence, we get that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$, as $k$ grows. This implies that the sequence $\{f_n\}_{n=1}^\infty$ converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$. In addition, from this argument it follows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
|\zeta|^{-\sigma}e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{\sigma,\Lambda}
for the corresponding $n$, showing that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
\begin{proposition}\label{prop:inclus-ge-exp}
If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, implying that
\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&\leq \|f\|_{\sigma,\Lambda'}.
In the last step, we use the assumption that $\Lambda' \le \Lambda$.
As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.\footnote{\textcolor{orange}{[footnote moved because of rephrasing above]} Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} 

@@

When $\sigma' > \sigma$, there's a continuous inclusion $\singexpalg{\sigma'}(\domain)\hookrightarrow \singexpalg{\sigma}(\domain)$.

@@

For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we are working in the space of holomprhic functions on $\domain$. In the topology of $\singexpalg{\sigma'}(\domain)$, this gives the desired continuos inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
\color{black}
\end{proof}
\section{Solving holomorphic Volterra equations}\label{sec:proof_main_results}
\subsection{Overview}
\color{blue}
\textcolor{orange}{[Revise and implement]}
\color{red}
The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$. In this section, we show that the method works by proving those results.

@@

\textcolor{red}{Now we know that} Therefore $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there. To confirm this, we will show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough. This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we will see in Section~\ref{sec:existence and uniqueness}.
\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
\subsubsection{Construction}\label{sec:construction}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
Rewrite $\solproto$ as $(1/p)\,\chi$, where
\[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right). \]
Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ \textcolor{blue}{simplifies} the calculation of $\hardpart \solproto$. For each $a \in \domain$,
\begin{align*}
\big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{1}{p}\,\chi\;d\zeta \\
& = - \frac{1}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p}\,\chi\;d\zeta\\
& = \frac{1}{p(a)} \int_{\zeta=0}^{a}\;d\chi \\
& = \frac{1}{p(a)} \left[ \chi(a) - \lim_{\zeta \to 0} \chi \right] \\
& = \solproto(a) - \frac{1}{p(a)} \lim_{\zeta \to 0} \chi.
\end{align*}
\textcolor{blue}{To prove that $\hardpart \solproto = \solproto$, we must now} show that $\lim_{\zeta \to 0} \chi = 0$.

By Condition~\eqref{cond:sing}, \textcolor{blue}{there exist} a radius $\delta>0$ and a constant $C$ such that
\begin{equation}\label{eqn:sing-bound}
\left|\frac{q}{p} + \frac{\tau}{\zeta}\right| < C
\end{equation}
whenever $|\zeta| < \delta$. \textcolor{red}{We can take advantage of} \textcolor{magenta}{We use this bound [we do not use the bound yet]} by rewriting the integral in the definition of $\chi$:
\begin{align*}
-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
\end{align*}
Exponentiating both sides, we see that
\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$. The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$. Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \chi = 0$. It follows, as discussed above, that $\hardpart \solproto = \solproto$. 
\color{orange}
For $\tau\in\C$
\begin{equation}
    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}\right)
\end{equation}
so if $\Re(\tau)>0$ and it is bigger than $\Im(\tau)$ the first term dominates in the limit $\zeta\to0$...but maybe we don't need ``bigger than $\Im(\tau)$", as ``we can rotate". I'm not very confortable with rotations, so probably I'll not add this complication. I'm also afraid we should be more carefull with these mooving domains, if we allow rotations. So maybe better not make things too complicated for the sake of generality. We have a good list of examples that fit in our pictures. 
\color{black}
\end{proof}
\subsubsection{Regularity}\label{sec:asymptotics}
%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, then we might simply have proof of Theorem \ref{thm:proto-growth} assuming only Condition \eqref{cond:diag-basic}. The proofs of the Proposition below can be combined together.}
Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We will prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
\begin{proposition}\label{prop:asymptotic at zero}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
\end{proposition}

>>>>

Throughout this paper, as described in Section~\ref{motivation}, the \textcolor{magenta}{``}position\textcolor{magenta}{'' [why are these quote marks nencessary? we've already introduced the term ``position'']} variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$. \textcolor{red}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$. Give $\cont(\domain)$ the compact-open topology, recalling that this} \textcolor{blue}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology. This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}. \textcolor{orange}{By the maximum principle and the connectedness of $\domain$, each of the seminorms $\sup_K |\cdot|$ is actually a norm.} The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.

@@

\par\color{blue}
For any $\sigma, \Lambda \in \R$, let
\[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ \textcolor{orange}{functions bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$}, equipped with the norm
\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]
With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K |\zeta|^\sigma e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
%%\textcolor{orange}{$\{f \in \holo(\domain) : f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}\}$}
\par\color{brown}

@@

Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{\sigma}{\Lambda}(\domain)$. This sequence is Cauchy in $\holo(\domain)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is bounded with respect to each of the seminorms on $\holo(\domain)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \domain$. Since $\holo(\domain)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\domain)$ will always converge in the topology of $\holo(\domain)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

The Cauchy property in $\singexp{\sigma}{\Lambda}(\domain)$ says that for any $r > 0$, there is some $n$ for which $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$. Since convergence in $\holo(\domain)$ implies pointwise convergence, it follows that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| \le r$. This reasoning shows that $f_1, f_2, f_3, \ldots$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$. It also shows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we have
\begin{align*}
|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{\sigma,\Lambda}
\end{align*}
for the corresponding $n$, so $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
\end{proof}
\color{red}
\begin{proposition}%%\label{exp-complete}
The space $\singexp{0}{\Lambda}(\domain)$ is complete.
\end{proposition}
\begin{proof}
Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

@@

\textcolor{pink}{Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.} \color{red} For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$. Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$. Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we \textcolor{red}{can} generalize Proposition~\ref{exp-complete}:
\color{brown}
For $\sigma\in\R$, let 
\[\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|\,,\qquad f\in\holo(\domain)\,.\]
\begin{definition}
    We define the normed space
    \[\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega):=\{f\in\holo(\domain)\,\vert \, \|f\|_{\sigma,\Lambda}<+\infty\}\,.\]
\end{definition}
\begin{rmk}
    The above is a space of functions uniformly bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda |\zeta|}$.
\end{rmk}
\color{black}
\color{pink}\begin{proposition}
The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
\end{proposition}
\color{brown}
\begin{proof}
Let $\{f_n\}_{n=1}^\infty\subset\singexp{\sigma}{\Lambda}(\domain)$ be a Cauchy sequence. The inclusion map $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each norm on $\sup_K |f|$ on $\holo(\domain)$, where $K \subset \Omega$ is compact. Hence, $\{f_n\}_{n=1}^\infty$ is a Cauchy sequence also in $\holo(\domain)$. The latter being complete~\cite[Proposition~3.5]{fnl-cpx-anal}, the sequence converges to a function $f\in\holo(\domain)$.

By the Cauchy property on $\singexp{\sigma}{\Lambda}(\Omega)$, for any $r > 0$ there exists $n$ such that $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ for every $k \ge n$. Since convergence in $\holo(\Omega)$ implies pointwise convergence, we get that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$, as $k$ grows. This implies that the sequence $\{f_n\}_{n=1}^\infty$ converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$. In addition, from this argument it follows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
\begin{align*}
|\zeta|^{-\sigma}e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
& \le r + \|f_n\|_{\sigma,\Lambda}
\end{align*}
for the corresponding $n$, showing that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
\end{proof}
\color{black}
\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
\begin{proposition}\label{prop:inclus-ge-exp}
If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{proposition}
\begin{proof}
By definition,
\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, implying that
\begin{align*}
\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&\leq \|f\|_{\sigma,\Lambda'}.
\end{align*}
In the last step, we use the assumption that $\Lambda' \le \Lambda$.
\end{proof}
One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}

\textcolor{violet}{As we mentioned in Section~\ref{sec:fn-space-defs} [now removed]}\textcolor{pink}{, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.}\footnote{\textcolor{orange}{[footnote moved because of rephrasing above]} \textcolor{pink}{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}}

@@

When $\sigma' > \sigma$, there is a continuous inclusion $\singexpalg{\sigma'}(\domain)\hookrightarrow \singexpalg{\sigma}(\domain)$.

@@

For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we are working in the space of holomprhic functions on $\domain$. In the topology of $\singexpalg{\sigma'}(\domain)$, this gives the desired continuos inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
\color{black}
\end{proof}
\section{Solving holomorphic Volterra equations}\label{sec:proof_main_results}
\subsection{Overview}
\color{blue}
In this section, we prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.

We first construct the prototype solution $\solproto$ from the kernel of $\hardpart$. We show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.

We then study how the perturbation $\softpart$ affects $\solproto$. We show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$. In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.
\par\textcolor{orange}{[Keep revising]} \color{red}
The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$. In this section, we show that the method works by proving those results.

@@

\textcolor{red}{Now we know that} \textcolor{brown}{Therefore} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there. To confirm this, we will show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough. This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we will see in Section~\ref{sec:existence and uniqueness}.
\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
\subsubsection{Construction}\label{sec:construction}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
Rewrite $\solproto$ as $(1/p)\,\chi$, where
\[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right). \]
Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ \textcolor{blue}{simplifies} the calculation of $\hardpart \solproto$. For each $a \in \domain$,
\begin{align*}
\big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{1}{p}\,\chi\;d\zeta \\
& = - \frac{1}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p}\,\chi\;d\zeta\\
& = \frac{1}{p(a)} \int_{\zeta=0}^{a}\;d\chi \\
& = \frac{1}{p(a)} \left[ \chi(a) - \lim_{\zeta \to 0} \chi \right] \\
& = \solproto(a) - \frac{1}{p(a)} \lim_{\zeta \to 0} \chi.
\end{align*}
\textcolor{blue}{To prove that $\hardpart \solproto = \solproto$, we must now} show that $\lim_{\zeta \to 0} \chi = 0$.

By Condition~\eqref{cond:sing}, \textcolor{blue}{there exist} a radius $\delta>0$ and a constant $C$ such that
\begin{equation}\label{eqn:sing-bound}
\left|\frac{q}{p} + \frac{\tau}{\zeta}\right| < C
\end{equation}
whenever $|\zeta| < \delta$. \textcolor{blue}{To use this bound, we rewrite the integral in the definition of $\chi$:} \textcolor{red}{We can take advantage of} \textcolor{magenta}{We use this bound [we do not use the bound yet]} \textcolor{pink}{by rewriting the integral in the definition of $\chi$:}
\begin{align*}
-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
\end{align*}
Exponentiating both sides, we see that
\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$. The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$. Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \chi = 0$. It follows, as discussed above, that $\hardpart \solproto = \solproto$. 
\color{orange}
For $\tau\in\C$
\begin{equation}
    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}\right)
\end{equation}
so if $\Re(\tau)>0$ and it is bigger than $\Im(\tau)$ the first term dominates in the limit $\zeta\to0$...but maybe we don't need ``bigger than $\Im(\tau)$", as ``we can rotate". I'm not very confortable with rotations, so probably I'll not add this complication. I'm also afraid we should be more carefull with these mooving domains, if we allow rotations. So maybe better not make things too complicated for the sake of generality. We have a good list of examples that fit in our pictures. 
\color{black}
\end{proof}
\subsubsection{Regularity}\label{sec:asymptotics}
%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, then we might simply have proof of Theorem \ref{thm:proto-growth} assuming only Condition \eqref{cond:diag-basic}. The proofs of the Proposition below can be combined together.}
Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We will prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
\begin{proposition}\label{prop:asymptotic at zero}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
\end{proposition}
